### 2018-03-21 Sections/about_the_authors.tex
Crypto, CV
Quantum simulation complete
Sc -> textsc

\comment{All photos must have same dimension (aspect ratio = 1)}

\comment{In order of authorship.}

\comment{Ask all authors for bios.}

\comment{Ask all authors for preferred high-res pic.}

\comment{Make sure all authors are listed}

@@

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney, Australia (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 50 publications and 1,300+ citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded {\sc BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

@@

\comment{Complete this section}x

>>>>

@@

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney, Australia (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 50 publications and 1,300+ citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded \textsc{BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

@@

### 2018-03-21 Sections/entanglement_the_ultimate_quantum_resource.tex
Sc -> textsc

Both scenarios involve Bell projections. These entangling measurements require active synchronisation to ensure that the measured qubits arrive at the entangling measurement device (typically a PBS) simultaneously, so as to achieve high HOM-visibility\index{HOM-visibility}, requiring synchronisation on the order of the photons' coherence length\index{Coherence length}. This can be achieved either using a brute-force {\sc Repeat-Until-Success} mode of operation (post-selecting on events where both qubits arrive within a required temporal window), or storing one qubit in quantum memory\index{Quantum memory} until the other arrives. However, post-selection is expensive, requiring a massive overhead in the number of trials, and quantum memory is technologically challenging to implement, more so in space.

>>>>

Both scenarios involve Bell projections. These entangling measurements require active synchronisation to ensure that the measured qubits arrive at the entangling measurement device (typically a PBS) simultaneously, so as to achieve high HOM-visibility\index{HOM-visibility}, requiring synchronisation on the order of the photons' coherence length\index{Coherence length}. This can be achieved either using a brute-force \textsc{Repeat-Until-Success} mode of operation (post-selecting on events where both qubits arrive within a required temporal window), or storing one qubit in quantum memory\index{Quantum memory} until the other arrives. However, post-selection is expensive, requiring a massive overhead in the number of trials, and quantum memory is technologically challenging to implement, more so in space.

### 2018-03-21 Sections/introduction.tex
Sc -> textsc

\begin{itemize}
	\item Searching unstructured databases:\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability \& optimisation problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal \textsc{3-SAT}\index{3-\textsc{SAT} problem} problem, are \textbf{NP}-complete.}\index{\textbf{NP} \& \textbf{NP}-complete}:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation problems}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm}:
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises Rivest, Shamir \& Adleman (RSA) public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Public-key encryption}, the most widely used cryptographic protocol on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation}:
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological big-data analysis:\index{Topological big-data analysis}
		\begin{itemize}
		\item Lloyd's algorthm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis; consumer behaviour; behavioural dynamics; neuroscience; and higher-dimensional signal and image processing.
		\end{itemize}
	\item Solving linear systems of equations:\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning:\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity.
		\item \textit{Ne obliviscaris}.
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

>>>>

\begin{itemize}
	\item Searching unstructured databases:\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability \& optimisation problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal 3-\textsc{SAT}\index{3-\textsc{SAT} problem} problem, are \textbf{NP}-complete.}\index{\textbf{NP} \& \textbf{NP}-complete}:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation problems}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm}:
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises Rivest, Shamir \& Adleman (RSA) public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Public-key encryption}, the most widely used cryptographic protocol on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation}:
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological big-data analysis:\index{Topological big-data analysis}
		\begin{itemize}
		\item Lloyd's algorthm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis; consumer behaviour; behavioural dynamics; neuroscience; and higher-dimensional signal and image processing.
		\end{itemize}
	\item Solving linear systems of equations:\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning:\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity.
		\item \textit{Ne obliviscaris}.
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

### 2018-03-21 Sections/multi_packet_operations.tex
Sc -> textsc

To accommodate such multi-packet operations, we must add some modifications to the QTCP protocol to handle:
\begin{itemize}
	\item Packet synchronisation\index{Packet synchronisation}: multiple packets subject to joint operations must be time-synchronised upon implementation of the joint operation. This might involve holding one packet in a quantum memory whilst waiting upon another. Thus, the time required to implement the joint operation is bottlenecked by the packet slowest to arrive.
	\item Bookkeeping of costs and attributes\index{Combining costs \& attributes}: when multiple packets are combined under some operation, how do error costs and attributes accumulate?
	\item Partner packet tracking\index{Partner packet tracking}: packets must keep track of the partner packets with which they are intended to undergo joint operations with. This may be achieved with the addition of {\sc Partners} fields in the packet headers, containing an array of their {\sc Message ID}'s.
	\item Operation signalling\index{Operation signalling}: the recipient node of multiple packets undergoing a joint operation must be informed as to what joint operations should be applied. This may be implemented via the addition of a {\sc What Operation} field to the header.
\end{itemize}

At a high level, these may be implemented in the {\sc Transport} layer as outlined in Alg.~\ref{alg:trans_multi_packet}, where we have intentionally left the functions for combining costs and attributes unspecified. In many instances, the \texttt{CombineCosts()} function could be as simple as a summation of its arguments.

>>>>

To accommodate such multi-packet operations, we must add some modifications to the QTCP protocol to handle:
\begin{itemize}
	\item Packet synchronisation\index{Packet synchronisation}: multiple packets subject to joint operations must be time-synchronised upon implementation of the joint operation. This might involve holding one packet in a quantum memory whilst waiting upon another. Thus, the time required to implement the joint operation is bottlenecked by the packet slowest to arrive.
	\item Bookkeeping of costs and attributes\index{Combining costs \& attributes}: when multiple packets are combined under some operation, how do error costs and attributes accumulate?
	\item Partner packet tracking\index{Partner packet tracking}: packets must keep track of the partner packets with which they are intended to undergo joint operations with. This may be achieved with the addition of \textsc{Partners} fields in the packet headers, containing an array of their \textsc{Message ID}'s.
	\item Operation signalling\index{Operation signalling}: the recipient node of multiple packets undergoing a joint operation must be informed as to what joint operations should be applied. This may be implemented via the addition of a \textsc{What Operation} field to the header.
\end{itemize}

At a high level, these may be implemented in the \textsc{Transport} layer as outlined in Alg.~\ref{alg:trans_multi_packet}, where we have intentionally left the functions for combining costs and attributes unspecified. In many instances, the \texttt{CombineCosts()} function could be as simple as a summation of its arguments.

### 2018-03-21 Sections/physical_architectures_for_quantum_computing.tex
Sc -> textsc

One of the key outcomes was that a {\sc Balanced} strategy\index{Balanced strategy} is optimal in terms of preparation rate. This is simply a strategy which preferentially always bonds clusters of equal length, beginning with the largest ones available. Asymmetric strategies, which bond clusters of differing lengths were found to be far less efficient.

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{linear_cluster_state_rates}
\caption{Linear micro-cluster preparation rates for three different types of entangling gates as described in \cite{bib:RohdeBarrett07}, against gate success probability, $p_\text{gate}$. Here a {\sc Balanced} fusion strategy is employed, whereby we only attempt to join clusters of equal length, always prioritising the largest ones available. This strategy was empirically found to perform better than any asymmetric strategies.}\label{fig:linear_cluster_state_r}
\end{figure}

@@

\subsubsection{{\sc BosonSampling}} \label{sec:BS} \index{Boson-sampling}

@@

\paragraph{The {\sc BosonSampling} model} \index{Boson-sampling model}

@@

For comparison, the equivalent classical protocol using distinguishable photons that evolve independently through the network would be described by,
\begin{align}
	P_{S,T} = \frac{\text{Per}(|U_{S,T}|^2)}{S_1!\dots S_m! T_1!\dots T_m!},
\end{align}
which yields a classically efficient sampling problem. Thus, for {\sc BosonSampling} the permanents are of complex-valued matrices, whereas for the equivalent classical problem the permanents are of positive real-valued matrices.

Very importantly, note that {\sc BosonSampling} does \textit{not} let us efficiently \textit{calculate} matrix permanents. Rather, it samples across a distribution of an exponential number of permanents. This is because, for an exponentially large sample space, with only a polynomial number of measurement trials, we are unlikely to gain more than binary accuracy about individual amplitudes, which is insufficient for determining any particular permanent. It appears that God knows how to efficiently solve matrix permanents, but conspires against us such that we remain ignorant of them. --- \textit{Deus magnus est.}

The size of a boson-sampler required to exhibit post-classicality is under active debate, as has undergone much historical revision \cite{RohdeRalph}. But some recent estimates suggest that as many as 50 photons in 2,500 modes might be a rough guide for such a threshold \cite{NoSupBS_Montanaro}. Needless to say, this is already an extremely challenging technological goal, suggesting that although the {\sc BosonSampling} problem is far simpler than universal LOQC, it is far from simple.

@@

\paragraph{Multiplexed {\sc BosonSampling}} \index{Multiplexed boson-sampling}

@@

The model is shown in Fig.~\ref{fig:multiplexed_bs}. We begin by operating $N$ SPDC sources in parallel. Clearly if $N$ is sufficiently large with respect to $n$, it becomes asymptotically certain that at least $n$ photons will be heralded. When this occurs, the successfully prepared $n$ photons -- in whatever configuration they happen to occur -- are routed to the first $n$ modes of the {\sc BosonSampling} interferometer $\hat{U}$ by the multiplexer (which is classically controlled by the SPDC heralding outcomes), and the protocol proceeds as usual.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{multiplexed_boson_sampling}
\caption{Model for multiplexed {\sc BosonSampling}. We operate \mbox{$N\gg n$} SPDC sources in parallel, which are multiplexed to the first $n$ modes of the interferometer $\hat{U}$. With sufficiently large $N$ it becomes asymptotically certain that at least $n$ single-photons will be heralded, thereby successfully preparing the desired {\sc BosonSampling} input state.} \label{fig:multiplexed_bs}\index{Multiplexed boson-sampling}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{multiplex_bs}
\caption{Probability of successfully preparing at least $n$ photons for {\sc BosonSampling} from a multiplexed source comprising a bank of $N$ SPDC sources in parallel. For sufficiently large $N$, we prepare the desired $n$ photons with probability asymptoting to unity.} \label{fig:multiplex_bs_res}\index{Multiplexed boson-sampling}
\end{figure}

However, although this procedure works in-principle, it comes at the expense of a large number of sources, $N$, and more challengingly, fast-feedforward. Keep in mind that if we were able to perform complex fast-feedforward, we might be able to do much more (and far more interesting things) than just {\sc BosonSampling} in the first place!

@@

\paragraph{Scattershot {\sc BosonSampling}} \index{Scattershot boson-sampling}

A variation on SPDC-based {\sc BosonSampling}, known as `scattershot'\index{Scattershot boson-sampling} {\sc BosonSampling}, has been presented \cite{bib:RandBS}, which obviates the difficultly of fast multiplexing in the approach described previously. Here, rather than inputting an SPDC source into the first $n$ of the $m$ modes, we input a source into \textit{every} mode, i.e $m$ sources in total. We then accept all events with $n$ heralding successes in total, irrespective of the configuration in which they occur. This has the effect of implementing $n$-photon {\sc BosonSampling} with an additional layer of randomisation on the input modes (i.e a randomisation in the input configuration, $T$, which is ordinarily fixed). However, since the algorithm is already randomised, this additional layer of randomisation does not undermine the complexity proofs, which hold as is. The scattershot model is shown in Fig.~\ref{fig:scattershot_model}.

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{scattershot_model}
\caption{Model for `scattershot' {\sc BosonSampling}. An SPDC source is inputted into all $m$ input modes. We post-select upon detecting a total of $n$ photons in the heralding modes, irrespective of their configuration, yielding an $n$-photon instance of {\sc BosonSampling} with randomised input configuration. Unlike multiplexed architectures, the scheme remains entirely passive, without requiring adaptive fast-feedforward.} \label{fig:scattershot_model}
\end{figure}

By keeping all configurations of $n$ photons, rather than just the \mbox{$\ket{T}=\ket{1}^{\otimes n} \ket{0}^{\otimes (m-n)}$} case, we effectively boost the $n$-photon heralding probability from,
\begin{align}
	P_n = \chi^{2n}(1-\chi^2)^n,	
\end{align}
to,
\begin{align}
	P_n = \binom{n^2}{n}\chi^{2n}(1-\chi^2)^{n^2},	
\end{align}
exhibiting a binomial enhancement in $n$-photon events, yielding a significant improvement in count-rates. For a given desired photon-number $n$, choosing the value for the squeezing parameter, $\chi$, which maximises $P_n$, we obtain the optimised success probability,
\begin{align}
	P_n^{(\text{opt})} \approx \frac{1}{e\sqrt{2\pi(n-1)}},
\end{align}
which exhibits only polynomial scaling against photon-number $n$, and is therefore scalable. This is shown in Fig.~\ref{fig:scattershot_probs}. This is in stark contrast to conventional {\sc BosonSampling}, where the success probability decays exponentially with photon-number, and is therefore inefficient. Importantly, unlike the multiplexed approach, this efficiency improvement does not require any active elements, remaining in the true spirit of {\sc BosonSampling}.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{scattershot_probs}
\caption{Probability of successfully implementing an instance of $n$-photon {\sc BosonSampling} using the scattershot technique, whereby all input modes are fed with an SPDC source, and all $n$-photon heralding events are accepted, irrespective of their configuration.} \label{fig:scattershot_probs}
\end{figure}

@@

Beyond photonic {\sc BosonSampling}, much investigation has explored the computational hardness of other types of linear optics sampling problems, using states beyond just single photons.

>>>>

One of the key outcomes was that a \textsc{Balanced} strategy\index{Balanced strategy} is optimal in terms of preparation rate. This is simply a strategy which preferentially always bonds clusters of equal length, beginning with the largest ones available. Asymmetric strategies, which bond clusters of differing lengths were found to be far less efficient.

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{linear_cluster_state_rates}
\caption{Linear micro-cluster preparation rates for three different types of entangling gates as described in \cite{bib:RohdeBarrett07}, against gate success probability, $p_\text{gate}$. Here a \textsc{Balanced} fusion strategy is employed, whereby we only attempt to join clusters of equal length, always prioritising the largest ones available. This strategy was empirically found to perform better than any asymmetric strategies.}\label{fig:linear_cluster_state_r}
\end{figure}

@@

\subsubsection{\textsc{BosonSampling}} \label{sec:BS} \index{Boson-sampling}

@@

\paragraph{The \textsc{BosonSampling} model} \index{Boson-sampling model}

@@

For comparison, the equivalent classical protocol using distinguishable photons that evolve independently through the network would be described by,
\begin{align}
	P_{S,T} = \frac{\text{Per}(|U_{S,T}|^2)}{S_1!\dots S_m! T_1!\dots T_m!},
\end{align}
which yields a classically efficient sampling problem. Thus, for \textsc{BosonSampling} the permanents are of complex-valued matrices, whereas for the equivalent classical problem the permanents are of positive real-valued matrices.

Very importantly, note that \textsc{BosonSampling} does \textit{not} let us efficiently \textit{calculate} matrix permanents. Rather, it samples across a distribution of an exponential number of permanents. This is because, for an exponentially large sample space, with only a polynomial number of measurement trials, we are unlikely to gain more than binary accuracy about individual amplitudes, which is insufficient for determining any particular permanent. It appears that God knows how to efficiently solve matrix permanents, but conspires against us such that we remain ignorant of them. --- \textit{Deus magnus est.}

The size of a boson-sampler required to exhibit post-classicality is under active debate, as has undergone much historical revision \cite{RohdeRalph}. But some recent estimates suggest that as many as 50 photons in 2,500 modes might be a rough guide for such a threshold \cite{NoSupBS_Montanaro}. Needless to say, this is already an extremely challenging technological goal, suggesting that although the \textsc{BosonSampling} problem is far simpler than universal LOQC, it is far from simple.

@@

\paragraph{Multiplexed \textsc{BosonSampling}} \index{Multiplexed boson-sampling}

@@

The model is shown in Fig.~\ref{fig:multiplexed_bs}. We begin by operating $N$ SPDC sources in parallel. Clearly if $N$ is sufficiently large with respect to $n$, it becomes asymptotically certain that at least $n$ photons will be heralded. When this occurs, the successfully prepared $n$ photons -- in whatever configuration they happen to occur -- are routed to the first $n$ modes of the \textsc{BosonSampling} interferometer $\hat{U}$ by the multiplexer (which is classically controlled by the SPDC heralding outcomes), and the protocol proceeds as usual.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{multiplexed_boson_sampling}
\caption{Model for multiplexed \textsc{BosonSampling}. We operate \mbox{$N\gg n$} SPDC sources in parallel, which are multiplexed to the first $n$ modes of the interferometer $\hat{U}$. With sufficiently large $N$ it becomes asymptotically certain that at least $n$ single-photons will be heralded, thereby successfully preparing the desired \textsc{BosonSampling} input state.} \label{fig:multiplexed_bs}\index{Multiplexed boson-sampling}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{multiplex_bs}
\caption{Probability of successfully preparing at least $n$ photons for \textsc{BosonSampling} from a multiplexed source comprising a bank of $N$ SPDC sources in parallel. For sufficiently large $N$, we prepare the desired $n$ photons with probability asymptoting to unity.} \label{fig:multiplex_bs_res}\index{Multiplexed boson-sampling}
\end{figure}

However, although this procedure works in-principle, it comes at the expense of a large number of sources, $N$, and more challengingly, fast-feedforward. Keep in mind that if we were able to perform complex fast-feedforward, we might be able to do much more (and far more interesting things) than just \textsc{BosonSampling} in the first place!

@@

\paragraph{Scattershot \textsc{BosonSampling}} \index{Scattershot boson-sampling}

A variation on SPDC-based \textsc{BosonSampling}, known as `scattershot'\index{Scattershot boson-sampling} \textsc{BosonSampling}, has been presented \cite{bib:RandBS}, which obviates the difficultly of fast multiplexing in the approach described previously. Here, rather than inputting an SPDC source into the first $n$ of the $m$ modes, we input a source into \textit{every} mode, i.e $m$ sources in total. We then accept all events with $n$ heralding successes in total, irrespective of the configuration in which they occur. This has the effect of implementing $n$-photon \textsc{BosonSampling} with an additional layer of randomisation on the input modes (i.e a randomisation in the input configuration, $T$, which is ordinarily fixed). However, since the algorithm is already randomised, this additional layer of randomisation does not undermine the complexity proofs, which hold as is. The scattershot model is shown in Fig.~\ref{fig:scattershot_model}.

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{scattershot_model}
\caption{Model for `scattershot' \textsc{BosonSampling}. An SPDC source is inputted into all $m$ input modes. We post-select upon detecting a total of $n$ photons in the heralding modes, irrespective of their configuration, yielding an $n$-photon instance of \textsc{BosonSampling} with randomised input configuration. Unlike multiplexed architectures, the scheme remains entirely passive, without requiring adaptive fast-feedforward.} \label{fig:scattershot_model}
\end{figure}

By keeping all configurations of $n$ photons, rather than just the \mbox{$\ket{T}=\ket{1}^{\otimes n} \ket{0}^{\otimes (m-n)}$} case, we effectively boost the $n$-photon heralding probability from,
\begin{align}
	P_n = \chi^{2n}(1-\chi^2)^n,	
\end{align}
to,
\begin{align}
	P_n = \binom{n^2}{n}\chi^{2n}(1-\chi^2)^{n^2},	
\end{align}
exhibiting a binomial enhancement in $n$-photon events, yielding a significant improvement in count-rates. For a given desired photon-number $n$, choosing the value for the squeezing parameter, $\chi$, which maximises $P_n$, we obtain the optimised success probability,
\begin{align}
	P_n^{(\text{opt})} \approx \frac{1}{e\sqrt{2\pi(n-1)}},
\end{align}
which exhibits only polynomial scaling against photon-number $n$, and is therefore scalable. This is shown in Fig.~\ref{fig:scattershot_probs}. This is in stark contrast to conventional \textsc{BosonSampling}, where the success probability decays exponentially with photon-number, and is therefore inefficient. Importantly, unlike the multiplexed approach, this efficiency improvement does not require any active elements, remaining in the true spirit of \textsc{BosonSampling}.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{scattershot_probs}
\caption{Probability of successfully implementing an instance of $n$-photon \textsc{BosonSampling} using the scattershot technique, whereby all input modes are fed with an SPDC source, and all $n$-photon heralding events are accepted, irrespective of their configuration.} \label{fig:scattershot_probs}
\end{figure}

@@

Beyond photonic \textsc{BosonSampling}, much investigation has explored the computational hardness of other types of linear optics sampling problems, using states beyond just single photons.

### 2018-03-21 Sections/quantum_algorithms.tex
Sc -> textsc

Such \textbf{NP}-complete algorithms can be quadratically enhanced in runtime using Grover's algorithm. To see this, note that all \textbf{NP}-complete problems can be efficiently mapped to one another with polynomial resource overhead (see Fig.~\ref{fig:complexity_classes}). Thus, we can restrict ourselves to considering the satisfiability problems\index{Satisfiability problems} discussed above -- the archetypal \textbf{NP}-complete problems. An example of the {\sc 3-SAT} problem\index{3-\textsc{SAT} problem }, which is \textbf{NP}-complete, is shown in Fig.~\ref{fig:3SAT}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{3SAT}
\caption{Digital circuit for an instance of the {\sc 3-SAT} problem. Each or the OR gates is input with some combination of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string. This problem is proven to be \textbf{NP}-complete.} \label{fig:3SAT}	
\end{figure}

@@

An equivalent quantum sampling problem would be to replace the pegs in the Galton board with beamsplitters, and the balls with photons. Now we have an analogous problem, but defined in terms of photonic wave-function amplitudes rather than classical transition probabilities. When generalised to the multi-photon context, this problem turns into the so-called {\sc BosonSampling}\index{Boson-sampling} problem, which is discussed in detail in Sec.~\ref{sec:BS}, a problem believed to not have an efficient classical simulation algorithm \cite{bib:AaronsonArkhipovBS}.

@@

Although not as obviously algorithmically useful as decision problems, sampling problems have received much interest owing to their generally very simple construction. For example, {\sc BosonSampling} requires only single-photon inputs, evolved via a passive linear optics\index{Linear optics} beamsplitter network, and measured using photo-detection\index{Photo-detection}. IQP sampling requires only single-qubit Hadamard gates\index{Hadamard gate} and generalised multi-qubit controlled-phase gates\index{Generalised controlled-phase gates}\footnote{Generalised CZ gates are simply gates diagonal in the logical basis, where the diagonal elements are arbitrary phases, \mbox{$\hat{U}_\text{CZ} = \text{diag}(e^{i\theta_1},\dots,e^{i\theta_n})$}.}, thereby sampling from the logical state,
\begin{align}
\ket{\psi_\text{out}} = \hat{H}^{\otimes n} \cdot \hat{U}_\text{CZs} \cdot \hat{H}^{\otimes n} \ket{0}^{\otimes n}.	
\end{align}
Because CZ gates commute, they can be performed in parallel, giving the IQP circuit construction very low circuit depth\index{Circuit depth}. The IQP protocol is shown in Alg.~\ref{alg:IQP_samp}.

>>>>

Such \textbf{NP}-complete algorithms can be quadratically enhanced in runtime using Grover's algorithm. To see this, note that all \textbf{NP}-complete problems can be efficiently mapped to one another with polynomial resource overhead (see Fig.~\ref{fig:complexity_classes}). Thus, we can restrict ourselves to considering the satisfiability problems\index{Satisfiability problems} discussed above -- the archetypal \textbf{NP}-complete problems. An example of the 3-\textsc{SAT} problem\index{3-\textsc{SAT} problem}, which is \textbf{NP}-complete, is shown in Fig.~\ref{fig:3SAT}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{3SAT}
\caption{Digital circuit for an instance of the 3-\textsc{SAT} problem, with input variables $\{x_i\}$. Each of the OR gates is input with some combination of 3 of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string $x$ that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string. This problem is proven to be \textbf{NP}-complete. Note that the similarly-defined 2-\textsc{SAT}\index{2-\textsc{SAT} problem} problem (i.e clauses each contain 2 input bits) is \textbf{P}, making 3-\textsc{SAT} the simplest model to consider in the study of \textbf{NP}-complete problems.} \label{fig:3SAT}	
\end{figure}

@@

An equivalent quantum sampling problem would be to replace the pegs in the Galton board with beamsplitters, and the balls with photons. Now we have an analogous problem, but defined in terms of photonic wave-function amplitudes rather than classical transition probabilities. When generalised to the multi-photon context, this problem turns into the so-called \textsc{BosonSampling}\index{Boson-sampling} problem, which is discussed in detail in Sec.~\ref{sec:BS}, a problem believed to not have an efficient classical simulation algorithm \cite{bib:AaronsonArkhipovBS}.

@@

Although not as obviously algorithmically useful as decision problems, sampling problems have received much interest owing to their generally very simple construction. For example, \textsc{BosonSampling} requires only single-photon inputs, evolved via a passive linear optics\index{Linear optics} beamsplitter network, and measured using photo-detection\index{Photo-detection}. IQP sampling requires only single-qubit Hadamard gates\index{Hadamard gate} and generalised multi-qubit controlled-phase gates\index{Generalised controlled-phase gates}\footnote{Generalised CZ gates are simply gates diagonal in the logical basis, where the diagonal elements are arbitrary phases, \mbox{$\hat{U}_\text{CZ} = \text{diag}(e^{i\theta_1},\dots,e^{i\theta_n})$}.}, thereby sampling from the logical state,
\begin{align}
\ket{\psi_\text{out}} = \hat{H}^{\otimes n} \cdot \hat{U}_\text{CZs} \cdot \hat{H}^{\otimes n} \ket{0}^{\otimes n}.	
\end{align}
Because CZ gates commute, they can be performed in parallel, giving the IQP circuit construction very low circuit depth\index{Circuit depth}. The IQP protocol is shown in Alg.~\ref{alg:IQP_samp}.
